Ages of Young Stars and Planets in the Kepler Field

### 2024-06-06 paper/ms.tex
update ms

\acknowledgements
This work was supported by the Heising-Simons 51~Pegasi~b Fellowship
(LGB, EKP)
and the Arthur R.~Adams SURF Fellowship (EKP).

>>>>

\acknowledgements

We are grateful to Kento Masuda for thought-provoking discussions 
which significantly influenced our thinking about this analysis.
The work itself was supported by the Heising-Simons 51~Pegasi~b Fellowship
(LGB, EKP)
and the Arthur R.~Adams SURF Fellowship (EKP).
